### 2019-02-27 papers/journal/prelim.tex
Added encodings for recahabilty for BMC implementation
asd

We will use lower case variables like $e,r,s$ etc to represent vectors of Boolean variables
possibly indexed with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas.
%
We will use the variables and the operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from variables in the formula to Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is
hard.
%

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem.
%

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use SAT/SMT/QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning(CDCL).
%
The QBF solver add support of quantifiers by adding more rules for
quantifiers.

>>>>

We will use lower case variables like $e,r,s$ etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is
known to be hard~\cite{sat-hard}.
%

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem~\cite{qbf-hard}.
%

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC/SMT/QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
%
The QBF solver add support of quantifiers by adding more rules for
quantifiers~\cite{qbf}.
